Governing through patronage: the bargain for education in decentralized Brazil

### 2022-08-31 paper/chapter_education.tex
feat: add literature

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/descriptive_enrollment.pdf}
    \caption{\textbf{Student enrollment by administration.}}
    \label{fig:enroll}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/descriptive_staff_breakdown}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/saeb_map.pdf}
    \caption{Uneven quality of municipal education. Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores. Averages are weighted by student participation rate.}
    \label{fig:saeb_map}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/descriptive_staff_breakdown.pdf}
    \caption{Proportion of public sector jobs by department}
    \label{fig:staff_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/hist_turnover_index.pdf}
    \caption{Distribution of turnover index by year, pooled across schools. Note that for robustness, only schools with more than 5 teachers are included.}
    \label{fig:hist_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/hist_coalition.pdf}
    \caption{Distribution of share of legislative seats allied with the mayor during the electoral campaign for the eletcoral period of 2002-2016.}
    \label{fig:hist_coalition}
\end{figure}

@@

\begin{landscape}
    \begin{table}[t]
      \centering
      \footnotesize
      \input{chapters/chapter_1/results/turnover_result}
      \caption{{\bf Executive coalitions and staff turnover.} An increase in the share of legislative seats held by the mayoral coalition decrease the amount of turnover for teachers and school principals, including hires or dismissals. Models 1 and 2 present results on the turnover index at the school level. Models 2 and 3 are aggregate hiring rates at the municipal level. Models 5 and 6 are logistic regressions at the individual, bureaucrat level. where the outcome of interest is the proportion of staff either hired or dismissed at a given year. Models 1, 3, and 5 include year and state fixed effects.}
      \label{tbl:turnover}
    \end{table}
\end{landscape}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/plot_coalition_coef_mun.pdf}
    \caption{{\bf Political alignment and staff turnover.} A visual representation of results presented in table \ref{tbl:turnover}. All models include year and state fixed effects.}
    \label{fig:coalition_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/plot_interactions_logit}
    \caption{\textbf{Differential reductions in patronage in teachers and school principals}. Predicted values for bureaucratic turnover plotted against the proportion of educational staff either hired or fired for any given year against the share of seats controlled by the executive.}
    \label{fig:turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/plot_coalition_coef_mun_second.pdf}
    \caption{\textbf{Patronage continues into the second term.} There is strong evidence that executive-legislative bargains continue into the mayor's second term. All models include a full set of controls, as well as year and state fixed effects.}
\end{figure}

@@

\begin{landscape}
    \begin{table}[t]
      \centering
      \footnotesize
      \input{chapters/chapter_1/results/student_learning.tex}
      \caption{{\bf Bureaucratic turnover and student learning} Teacher and school principal turnover have a negative effect on student learning. Models 1 and 2 present results for teacher turnover index constructed at the school level. Models 3 and 4 estimate the effect of new teachers and school principals entering the school (less than two years). All models include year and state fixed effects.}
      \label{tbl:student_learning}
    \end{table}
\end{landscape}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/model_turnover_learning.pdf}
  \caption{{\bf Bureaucratic turnover and student learning} Teacher and school principal turnover have a negative effect on student learning, across different sets of exams (\emph{SAEB} and \emph{SPAECE}). All models include a full set of controls, as well as year and state fixed effects.}
  \label{fig:hlm_mods}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{chapters/chapter_1/plots/reelection_marginal_effect_plots.pdf}
    \caption{\textbf{Differential returns to patronage}. Mayors who engage in patronage do not directly benefit from it. Instead, city councilors in the mayoral ally base seem to be benefiting from it at the expense of non-allied city councilors.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics{chapters/chapter_1/plots/covariate_balance.pdf}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics{chapters/chapter_1/plots/accountability_fit.pdf}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\linewidth]{chapters/chapter_1/plots/visual_rdd_legislative_seat_flip.pdf}
\end{figure}

% \blue{chapters/chapter_1/plots/balance_hlm}

@@

% \blue{chapters/chapter_1/plots/balance_felm.pdf}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/descriptive_enrollment.pdf}
    \caption{\textbf{Student enrollment by administration.}}
    \label{fig:enroll}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/descriptive_staff_breakdown}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/saeb_map.pdf}
    \caption{Uneven quality of municipal education. Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores. Averages are weighted by student participation rate.}
    \label{fig:saeb_map}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/descriptive_staff_breakdown.pdf}
    \caption{Proportion of public sector jobs by department}
    \label{fig:staff_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/hist_turnover_index.pdf}
    \caption{Distribution of turnover index by year, pooled across schools. Note that for robustness, only schools with more than 5 teachers are included.}
    \label{fig:hist_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/hist_coalition.pdf}
    \caption{Distribution of share of legislative seats allied with the mayor during the electoral campaign for the eletcoral period of 2002-2016.}
    \label{fig:hist_coalition}
\end{figure}

@@

\begin{landscape}
    \begin{table}[t]
      \centering
      \footnotesize
      \input{results/turnover_result}
      \caption{{\bf Executive coalitions and staff turnover.} An increase in the share of legislative seats held by the mayoral coalition decrease the amount of turnover for teachers and school principals, including hires or dismissals. Models 1 and 2 present results on the turnover index at the school level. Models 2 and 3 are aggregate hiring rates at the municipal level. Models 5 and 6 are logistic regressions at the individual, bureaucrat level. where the outcome of interest is the proportion of staff either hired or dismissed at a given year. Models 1, 3, and 5 include year and state fixed effects.}
      \label{tbl:turnover}
    \end{table}
\end{landscape}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun.pdf}
    \caption{{\bf Political alignment and staff turnover.} A visual representation of results presented in table \ref{tbl:turnover}. All models include year and state fixed effects.}
    \label{fig:coalition_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_interactions_logit}
    \caption{\textbf{Differential reductions in patronage in teachers and school principals}. Predicted values for bureaucratic turnover plotted against the proportion of educational staff either hired or fired for any given year against the share of seats controlled by the executive.}
    \label{fig:turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun_second.pdf}
    \caption{\textbf{Patronage continues into the second term.} There is strong evidence that executive-legislative bargains continue into the mayor's second term. All models include a full set of controls, as well as year and state fixed effects.}
\end{figure}

@@

\begin{landscape}
    \begin{table}[t]
      \centering
      \footnotesize
      \input{results/student_learning.tex}
      \caption{{\bf Bureaucratic turnover and student learning} Teacher and school principal turnover have a negative effect on student learning. Models 1 and 2 present results for teacher turnover index constructed at the school level. Models 3 and 4 estimate the effect of new teachers and school principals entering the school (less than two years). All models include year and state fixed effects.}
      \label{tbl:student_learning}
    \end{table}
\end{landscape}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\linewidth]{plots/model_turnover_learning.pdf}
  \caption{{\bf Bureaucratic turnover and student learning} Teacher and school principal turnover have a negative effect on student learning, across different sets of exams (\emph{SAEB} and \emph{SPAECE}). All models include a full set of controls, as well as year and state fixed effects.}
  \label{fig:hlm_mods}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/reelection_marginal_effect_plots.pdf}
    \caption{\textbf{Differential returns to patronage}. Mayors who engage in patronage do not directly benefit from it. Instead, city councilors in the mayoral ally base seem to be benefiting from it at the expense of non-allied city councilors.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics{plots/covariate_balance.pdf}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics{plots/accountability_fit.pdf}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\linewidth]{plots/visual_rdd_legislative_seat_flip.pdf}
\end{figure}

% \blue{plots/balance_hlm}

@@

% \blue{plots/balance_felm.pdf}
